Road Segment Prioritization for Bicycle Infrastructure

### 2020-10-30 README.Rmd

The methodologies in Section **How do I cite a section??** are underpinned by different ethical principles, even though these principles are not explicitly acknowledged by the authors. This is important since different ethical principles constitute different problem formulations and targets. Broadly speaking, transport appraisal can be based on either utilitarian or egalitarian principles. The former seeks to maximize the overall benefit, while the latter is concerned with a fair distribution of benefits [@jafino2020transport]. @nahmias2017integrating criticize the utilitarian approach that has been historically popular in the evaluation of transport investments, explaining how the maximization of overall benefit fails to account for the distribution of that benefit among communities or individuals. @lucas2016method explain how transport studies have traditionally looked at the bigger picture without studying the distribution of investments on the different parts of the study area, and go on to propose an egalitarian approach that ensures the dis-aggregation of transport policy benefits across the study area. @pereira2017distributive also emphasize the need for a more egalitarian approach to transport planning. They highlight accessibility as a cornerstone of distributive justice, and contend that policies should aim to distribute investments in a way that minimizes spatial variations in accessibility. This research attempts to provide a methodology that is grounded in egalitarian principles. **Write some more here**

>>>>

The methodologies in Section \@ref(planning-cycling-networks) are underpinned by different ethical principles, even though these principles are not explicitly acknowledged by the authors. This is important since different ethical principles constitute different problem formulations and targets. Broadly speaking, transport appraisal can be based on either utilitarian or egalitarian principles. The former seeks to maximize the overall benefit, while the latter is concerned with a fair distribution of benefits [@jafino2020transport]. @nahmias2017integrating criticize the utilitarian approach that has been historically popular in the evaluation of transport investments, explaining how the maximization of overall benefit fails to account for the distribution of that benefit among communities or individuals. @lucas2016method explain how transport studies have traditionally looked at the bigger picture without studying the distribution of investments on the different parts of the study area, and go on to propose an egalitarian approach that ensures the dis-aggregation of transport policy benefits across the study area. @pereira2017distributive also emphasize the need for a more egalitarian approach to transport planning. They highlight accessibility as a cornerstone of distributive justice, and contend that policies should aim to distribute investments in a way that minimizes spatial variations in accessibility. This research attempts to provide a methodology that is grounded in egalitarian principles. **Write some more here**
